Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2017-01-27 manuscript.tex
latest

 Unlike the abstract population-genetic relative fitnesses $w_i$, the lottery model $b_i$ and $c_i$ have a mechanistic interpretation in terms of fecundity and territorial contests, while overlapping generations allows for genotypic differences in longevity. Note, however, that the classic lottery model, and the present work, ignore the stochastic drift in type frequencies (large $T$ approximation), which is the focus of the Wright-Fisher model.

>>>>

The main advantage of the classic lottery model for our purposes here is that the abstract population-genetic relative fitnesses $w_i$ can be replaced with more ecologically-grounded fecundity, competitive ability and mortality parameters $b_i$, $c_i$ and $d_i$. In particular, differences in individual longevity are only possible because generations are overlapping. However, note that the classic lottery model, and the present work, ignore the stochastic drift in type frequencies (large $T$ approximation) which is the focus of the Wright-Fisher model.
